### 2014-11-13 tex/evaluation.tex
Completed text for the evaluation section

\begin{figure*}[t]
%\begin{table} [t]
  \centering
  \begin{tabular}{| c | c | r | r | r | r | r | r | r | r | r |}
  \hline
   \multirow{2}{*}{Method }&\multirow{2}{*}{ $k$ }
   &\multicolumn{3}{|c|}{Time} &\multicolumn{3}{|c|}{States} &\multicolumn{3}{|c|}{ Paths }\\
								&	&\gsetxt{} & LS		&SH		&\gsetxt{}	& LS & SH&\gsetxt{}	& LS & SH\\
   \hline
    \multirow{3}{*}{LinkedList }			&3	& 0.91	& 1.21	& 0.69	& 2465	& 2844	& 99		&1656	& 1269	& 25\\
   		 						& 4	& 2.92	& 3.35	& 0.91	& 25774	& 29977	& 155	&17485	& 13550	& 39\\
   								& 5	& 20.78	& 19.47	& 1.59	& 341164	& 400296	& 223	&232743	& 181849	& 56\\
								& 6	& 280.56	& 299.19	& 2.36	&5447980	&6437201	& 303	&3731094	&2933027	& 76\\
    \hline
    \multirow{3}{*}{BinarySearchTree }	& 1	& 0.26	& 0.28	& 0.36	& 19		& 23		& 29		& 6		& 6		& 6\\
   		 						& 2	& 0.83	& 1.28	& 0.93	& 143	& 143	& 145	& 43		& 42		& 33\\
   								& 3	& 20.63	& 25.55	& 4.03	& 1953	& 1703	& 1485	& 515	& 515	& 328\\
    \hline
      \multirow{3}{*}{TreeMap}			& 1	& 0.47	& 0.52	& 0.77	& 65		& 70		& 215	& 11		& 11		& 11\\
   		 						& 2	& 8.99	& 9.73	& 4.72	& 1009	& 942	& 3219	& 127	& 122	& 73\\
   								& 3	& -		& -		& 145.56	& -		& -		& 78695	& -		& -		& 887\\

    \hline
  \end{tabular}
  \caption{test results}
  \label{tab:results}
%\end{table}
\end{figure*}

\subsection{Analysis}

The results ofAs expected, the repeated use of lazy initialization throughout the program causes an exponential increase in the number of paths explored by \gsetxt{}. By combining many of the \gsetxt{} paths, \symtxt{} avoids the exponential path explosion, demonstrating dramatically reduced, though still exponential, execution time growth. Remarkably, path growth in the k-bound appears to be sub-linear.

While the BinarySearchTree example introduces integer constraints, \symtxt{} performance does not appear to suffer due to the constraint burden. Indeed, at k=3, there appears to be a significant performance advantage in favor of \symtxt{}.

The TreeMap example has a large number of integer compare instructions, and so it should present the greatest challenge to the constraint solver. Despite this, \symtxt{} still explores fewer paths than \gsetxt{}, and \gsetxt{} notably failed to terminate within the allotted time bounds for the $k=3$ test case.

>>>>

%\begin{figure*}[t]
\begin{table*} [t]
  \centering
  \begin{tabular}{| c | c | r | r | r | r | r | r | r | r | r |}
  \hline
   \multirow{2}{*}{Method }&\multirow{2}{*}{ $k$ }
   &\multicolumn{3}{|c|}{Time} &\multicolumn{3}{|c|}{States} &\multicolumn{3}{|c|}{ Paths }\\
								&	&\gsetxt{} & L\#		&SL		&\gsetxt{}	& L\# & SL&\gsetxt{}	& L\# 	& SL\\
   \hline
    \multirow{3}{*}{LinkedList }			&3	& 0.91	& 1.21	& 0.69	& 2465	& 2844	& 99		&1656	& 1269	& 25\\
   		 						& 4	& 2.92	& 3.35	& 0.91	& 25774	& 29977	& 155	&17485	& 13550	& 39\\
   								& 5	& 20.78	& 19.47	& 1.59	& 341164	& 400296	& 223	&232743	& 181849	& 56\\
								& 6	& 280.56	& 299.19	& 2.36	&5447980	&6437201	& 303	&3731094	&2933027	& 76\\
    \hline
    \multirow{3}{*}{BinarySearchTree }	& 1	& 0.26	& 0.28	& 0.36	& 19		& 23		& 29		& 6		& 6		& 6\\
   		 						& 2	& 0.83	& 1.28	& 0.93	& 143	& 143	& 145	& 43		& 42		& 33\\
   								& 3	& 20.63	& 25.55	& 4.03	& 1953	& 1703	& 1485	& 515	& 515	& 328\\
    \hline
      \multirow{3}{*}{TreeMap}			& 1	& 0.47	& 0.52	& 0.77	& 65		& 70		& 215	& 11		& 11		& 11\\
   		 						& 2	& 8.99	& 9.73	& 4.72	& 1009	& 942	& 3219	& 127	& 122	& 73\\
   								& 3	& -		& -		& 145.56	& -		& -		& 78695	& -		& -		& 887\\

    \hline
  \end{tabular}
  \caption{test results}
  \label{tab:results}
\end{table*}
%\end{figure*}

\subsection{Analysis}
The results of the experiments are presented in Table \ref{tab:results}. The rows contain to individual $k$-bounded test runs for each of the evaluated programs. The columns show the run time, state count and path count for each of the three algorithms tested. The headings \gsetxt{}, L\#, and SL correspond to the Generalized Symblic Execution, lazier\#, and \symtxt{} algorithms, respectively. Table entries containing - correspond to test runs that exceeded the allotted time bounds.

In agreement with the theoretical results, the number of paths explored by \symtxt{} is strictly less than or equal the number of paths explored by \gsetxt{} for any given test run. Curiously, the same relationship does not hold true for states. State counts can vary between algorithms, because states in JPF represent points of nondeterminism, and each algorithm differs in this regard. For example, \gsetxt{} has additional points of nondeterminism during field reads, but in contrast address compares are completely deterministic. Thus, in example programs with large numbers address compares, such as TreeMap, state counts for lazier\# and \symtxt{} may exceed those for \gsetxt{}. Despite this, in practice this is often mitigated by the fact that symtxt{} can dispatch address compares without consulting the constraint solver.

Run times for most tests strongly favor \symtxt{}, especially LinkedList example. In fact, a number of test cases can be efficiently completed using \symtxt{} for k-bounds that are not practical to be attempted with \gsetxt{} or lazier\#, including the BinarySearchTree for $k=4$ and LinkedList for $k=8$. Some of this discrepancy may be accounted for by the fact that \symtxt{} is equipped for incremental solving, however, in informal testing with the incremental solver turned off, \symtxt{} usually performed better than \gsetxt and lazier\#, especially in test runs with high k-bounds.
